\subsection{Working Together}
In \ac{DST}, a multi-player game, players will often come across each other and may work together in order to achieve a goal (e.g. defeating a giant).
Working together may become a substantial part of the agents activities.
Thus, it is important to understand how agents can work together.

\subsubsection{Joint Intentions}
What is involved when a group of people decide to do something together?
Joint action by a team involves more than just the union of simultaneous individual actions, even when those actions are coordinated. We would not say that there is any team work involved in ordinary automobile traffic, even though the drivers act simultaneously and are coordinated by the traffic signs and rules of the road.

But when a group of drivers decide to do something together, such as driving somewhere as a convoy, it appears that the group acts as a single agent with beliefs, goals, and intentions of its own, over and above the individual ones.
Levesque proposed a formal model of these mental properties of a group, and especially how joint intentions to act affect and are affected by (and ultimately reduce to) the mental states of the participants \cite{levesque:joint-intention}.

In his work, Levesque argues that groups of agents have joint intentions.

\subsubsection{SharedPlan}

\subsubsection{STEAM}
STEAM is an implemented general model of teamwork based on \textit{joint intentions} theory \cite{levesque:joint-intention} and the \textit{SharedPlans}\footnote{This theory is based on a intentional attitude, \textit{intending that}, which represents an agent's intention towards its collaborator's actions.} theory \cite{grosz:sharedplan}.

STEAM starts with joint intentions but then builds up hierarchical structures that parallel the SharedPlans theory, particularly, partial SharedPlans.
The result is a hybrid model of teamwork, that borrows from the strengths of both joint intentions (formalization of commitments in building and maintaining joint intentions) and SharedPlans (detailed treatment of team's attitudes in complex tasks, as well as unreconciled tasks).